LAGOS lake depth

### 2020-04-29 manuscript/figures.Rmd
cleanup predictor table

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth predictor variables for modelling efforts (and for lakes continent-wide).", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{2}

>>>>

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r 01_predictors, fig.cap = "Table 1: Summary of lake depth and predictor variables for modelling efforts (and for lakes in the contiguous United States from <LAGOSUS-Depth citation>). Predictor variables used in Eq 2 are printed in bold face. Dashes (-) indicate identical sample size among this study and that of the contiguous United States.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../tables/01_predictors.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{2}

### 2020-04-29 tables/01_predictors.Rmd
cleanup predictor table

```{r predictors_table}
# setwd("figures")
dt <- dt_combined %>%
  dplyr::filter(str_detect(variable, 
                           "^lake_|^ws_lake_arearatio|^dist_|_slope")) %>%
  dplyr::filter(!str_detect(variable,
                      "totalarea|islandperimeter|between|buffer100m")) # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

>>>>

```{r predictors_table}
# setwd("figures")
dt <- dt_combined %>%
  dplyr::filter(str_detect(variable, 
                           "^lake_|^ws_lake_arearatio|^dist_|_slope")) %>%
  dplyr::filter(!str_detect(variable,
                      "totalarea|islandperimeter|between|buffer100m|lake_meandepth_m")) # %>%
  # mutate(n = dt_bathy$n[which(dt_bathy$variable == "inlake_slope")])

@@

dt <- dplyr::rename(dt, Variable = variable)

# bold Eq 2 predictor variables
dt$Variable[!stringr::str_detect(dt$Variable, "slope|distance|depth")] <- 
  paste0("**", 
         dt$Variable[!stringr::str_detect(dt$Variable, "slope|distance|depth")],
         "**")
